---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gist

<!-- badges: start -->
<!-- badges: end -->

The gist package provides a set of functions to work with the GitHub Gist API. It allows you to create, read, update and delete gists. Moreover, it provides a shiny app to interact with gists. The app will be installed as an addin and can be accessed via the RStudio addin menu.

## Installation

You can install the development version of gist like so:

```{r, eval=FALSE}
devtools::install_github("edgar-treischl/gist")
```

In order to retrieve data, you need to provide a GitHub API token (`github_api`) with the `keyring` package. Use the `key_set()` function code to save the token:

```{r, eval=FALSE}
#Save GitHub API token as github_api
keyring::key_set(service = "github_api")
```


## Example

Go to the addin menu or use the following code to open the gist app:

```{r, eval=FALSE}
#Run gist_addin()
gist::gist_addin()
```

